Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-23 2016_ICML/cmrs.tex
Fixing issue reported by ICML paper checker

\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

@@

The second class of acquisition functions are \emph{improvement-based policies}, such as the probability of improvement \citep[PI,][]{kushner_new_1964} over the current best value, which can be calculated in closed-form for a GP model:
$$a_{PI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{P}[f(\mathbf{x}) > \tau] = \Phi(\gamma(\mathbf{x})),$$
where $\gamma(x) = (\mu_n(\mathbf{x}) - \tau) / \sigma_n(x)$, $\Phi(\cdot)$ denotes the cumulative distribution function of the
standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max_i y_i$.
Since PI is known to exploit quite aggressively \cite{jones_taxonomy_2001}, a more popular
alternative is the \emph{expected improvement} \citep[EI,][]{mockus_application_1978} over the
current best value, which can again be computed in closed form for a GP model:
\begin{equation*}
\begin{split}
 a_{EI}(\mathbf{x}; \mathcal{D})
  & := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)] \\
  &  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right),
\end{split}
\end{equation*}
where $\phi(\cdot)$ denotes the standard Gaussian density function.  A
generalization of EI is the \emph{knowledge gradient} factor \cite
{frazier_knowledge-gradient_2009}, which can better handle noisy observations,
which impede the estimation of the incumbent. The knowledge gradient requires
defining a set $A_n$ from which one would choose the final solution.

>>>>

\usepackage{hyperref}
\usepackage{url}

@@

The second class of acquisition functions are \emph{improvement-based policies}, such as the probability of improvement \citep[PI,][]{kushner_new_1964} over the current best value, which can be calculated in closed-form for a GP model:
$$a_{PI}(\mathbf{x}; \mathcal{D}_n) := \mathbb{P}[f(\mathbf{x}) > \tau] = \Phi(\gamma(\mathbf{x})),$$
where $\gamma(x) = (\mu_n(\mathbf{x}) - \tau) / \sigma_n(x)$, $\Phi(\cdot)$ denotes the cumulative distribution function of the
standard Gaussian, and $\tau$ denotes the incumbent, typically the best function value observed so far: $\tau = \max_i y_i$.
Since PI exploits quite aggressively \cite{jones_taxonomy_2001}, a more popular
alternative is the \emph{expected improvement} \citep[EI,][]{mockus_application_1978} over the
current best value $ a_{EI}(\mathbf{x}; \mathcal{D}) := \mathbb{E}[(f(x) - \tau)\mathbb{I}(f(x) > \tau)]$, which can again be computed in closed form for a GP model as
$a_{EI}(\mathbf{x}; \mathcal{D})
  = \sigma_n(\mathbf{x})\left(\gamma(\mathbf{x})\Phi(\gamma(\mathbf{x})) + \phi(\gamma(\mathbf{x}))\right)$,
where $\phi(\cdot)$ denotes the standard Gaussian density function.  A
generalization of EI is the \emph{knowledge gradient} factor \cite
{frazier_knowledge-gradient_2009}, which can better handle noisy observations,
which impede the estimation of the incumbent. The knowledge gradient requires
defining a set $A_n$ from which one would choose the final solution.
